Unicode Implementation Issues \thanks { This is a working document for the Rexx Language Association (RexxLA). There will be one or more separate requirements documents. It is written in \LaTeX\ \fmtversion\ and was rendered \today\ using \enginedetails. }

### 2023-10-27 ARB/standards/work-in-progress/unicode/Unicode.Implimentation.tex
Add files via upload
More cross-references to RXU

The RXU preprocessor accepts \textbf{OPTIONS DEFAULTSTRING} \textit{default}, where default can be one of \textbf{ BYTES},\textbf{ CODEPOINTS}, \textbf{TEXT} OR \textbf{NONE}.

@@

RXU has five tpes of string literals:
\begin{definition}
\item['string'] The type is determined by OPTIONS.
\item['string'P] Unicode by code point
\item['string'T] Unicode by EGC
\item['space separated tokens'U] Unicode code points by alias, name or value
\item['string'Y] Legacy bYte string
\end{definition}

>>>>

\subsubsection{RXU OPTIONS values}

The RXU preprocessor accepts these\cite{RXU:OPT} values on the OPTIONS statement:

\begin{definition}
\item[DEFAULTSTRING \textit{default}] where \textit{default} determines the type of a string literal with no suffix:
\begin{definition}
\item[\underline{BYTES}]Y
\item[CODEPOINTS]P
\item[NONE]
\item[TEXT]T
\end{definition}
\item[COERCIONS \textit{ucoercion}] where \textit{ucoercion} determines the result of an operation on strings of mixed string types:
\begin{definition}
\item[DEMOTE]Type of lowest operand
\item[LEFT]Type of left operand
\item[NONE]Raise SYNTAX
\item[\underline{PROMOTE}]Type of highest operand
\item[RIGHT]Type of right operand
\end{definition}
\end{definition}

@@

\subsubsection{RXU string types}

RXU has five types of string literals\cite{RXU:NewTypes}:
\begin{definition}
\item['string'] The type is determined by OPTIONS.
\item['string'P] Unicode by code point
\item['string'T] Unicode by EGC
\item['space separated tokens'U]
Unicode code points by alias, name or hexadecimal value;
the string is BYTES rather than CODEPOINTS or TEXT.
\item['string'Y] Legacy bYte string,can only be promoted if valid UTF-8 sequences
\end{definition}
